### 2020-05-10 ncov.tex
the

We ran 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps using Metropolis-Hastings algorithm.
Proposal distributions are modeled using independent normal distributions.
Initial values and variances of the proposal distributions are chosen by trial-and-error to ensure a reasonable acceptance rate (around 10\%) and convergence within 1,000,000 steps.
Posterior samples are thinned every 1000 steps to remove autocorrelations among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01  \citep{gelman1992inference} and the effective sample size is greater than 1000 for all hyperparameters ($\mu_r, \mu_G, \mu_\kappa, \sigma_r, \sigma_G, \sigma_\kappa$);
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by computing 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each hyperparameter.

>>>>

We run 4 independent Markov Chain Monte Carlo chains each consisting of 500,000 burnin steps and 500,000 sampling steps using the Metropolis-Hastings algorithm.
Proposal distributions are modeled using independent normal distributions.
Initial values and variances of the proposal distributions are chosen by trial-and-error to ensure a reasonable acceptance rate (around 10\%) and convergence within 1,000,000 steps.
Posterior samples are thinned every 1000 steps to remove autocorrelations among posterior samples.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01  \citep{gelman1992inference} and the effective sample size is greater than 1000 for all hyperparameters ($\mu_r, \mu_G, \mu_\kappa, \sigma_r, \sigma_G, \sigma_\kappa$);
trace plots and marginal posterior distribution plots are presented in Appendix.
95\% credible intervals (CI) are calculated by computing 2.5\% and 97.5\% quantiles from the marginal posterior distribution for each hyperparameter.
